Manuscript Figures

### 2020-06-19 doc/MS_Figures.rmd
working on figures

#load(file="~./MLH1repo/data/CleanBivData_6.3.20.RData")

#
#load(file="~./MLH1repo/data/total_SC_30.12.19.RData")

#skeletonize - this is the total sc file
#SC.skel = read.csv("~./MLH1repo/data/SCskel_output_feb20.csv", header = TRUE, strip.white = TRUE)

@@

DMC1.boxplot <- ggplot(aes(x=strain, y=total.count, color=stage), data=DMC1.DF[DMC1.DF$stage != "P",])+
  geom_boxplot(alpha=.5) +geom_jitter() +

>>>>

@@

#aes(x=strain, y=total.count, color=stage

DMC1.boxplot <- ggplot( aes(x=strain, y=total.count, color=stage), data=DMC1.DF[DMC1.DF$stage != "P",])+

  #stat_boxplot( aes(x=strain, y=total.count, color=stage), 
 #   geom='errorbar', linetype=1, width=0.5)+

  geom_boxplot( aes(x=strain, y=total.count),outlier.shape = NA, alpha=.5 )+

  geom_jitter() +

### 2020-06-19 doc/MS_Figures_v2.rmd
working on figures

DMC1.boxplot <- ggplot(aes(x=strain, y=total.count, color=stage), data=DMC1.DF[DMC1.DF$stage != "P",])+
  geom_boxplot(alpha=.5) +geom_jitter() +

    labs(y = "DMC1 count per Cell")+

@@

#"#E69F00" orange
#"#0072B2" darker blue

>>>>

#remoe outliers, with outlier shape

DMC1.boxplot <- ggplot(aes(x=strain, y=total.count, color=stage), data=DMC1.DF[DMC1.DF$stage != "P",])+

  geom_boxplot(alpha=.5, outlier.shape = NA) +

  #Yeah, I can dodge the points!!
  geom_point(pch = 19, position = position_jitterdodge()) +
  #geom_jitter() +

    labs(y = "DMC1 Count per Cell")+

@@

#"#E69F00" orange
#"#0072B2" darker blue
```
